Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-14 sections/01-introduction.tex
Update on Overleaf.

The evaluation of measurement, prediction and forecasting methods become increasingly important and sophisticated, as technologies and data availability enable their application in more and more areas. While introducing new medical measurement methods already requires a comprehensive evaluation and comparison with established standard measurement methods to ensure their validity and reliability, it is generally essential for forecasts and nowcasting methods to assess the extent to which the predictions correspond to the development of reality. Conventionally, the methods are evaluated using distance measures that take aggregated local absolute differences between predictions (or measurements) and target values into account. For example, the continuously ranked probability score (CRPS) can be used to evaluate the accuracy of probabilistic predictions. %It is also based on the integrated squared differences between the cumulative distribution function (CDF) of the prediction and the Heaviside jump function. 
These measures all fail to consider whether the right direction of change is being taken, which can often be highly relevant in practice. The information about whether an estimator, be it a measurement device, forecast, or nowcast, can accurately predict an increase or decrease is crucial when taking decisions based  on  the estimator's prediction results. In the following, we provide an overview of the characteristics and evaluations of measurement, forecasting and nowcasting methods and show their relationships to trending.

@@

As outlined above, trending evaluation is crucial for measurements, predictions, and forecasts. 
However, regardless of the application domain, most conventional method comparisons and evaluations consider local absolute differences in different ways without directly assessing whether the correct direction of change is output.

>>>>

The evaluation of measurement, prediction, and forecasting methods become increasingly important and sophisticated as technologies and data availability enable their application in more and more areas. While introducing new medical measurement methods already requires a comprehensive evaluation and comparison with established standard measurement methods to ensure their validity and reliability, it is generally essential for forecasts and nowcasting methods to assess the extent to which the predictions correspond to the development of reality. Conventionally, the methods are evaluated using distance measures that take aggregated local absolute differences between predictions (or measurements) and target values into account. For example, the continuously ranked probability score (CRPS) can be used to evaluate the accuracy of probabilistic predictions. %It is also based on the integrated squared differences between the cumulative distribution function (CDF) of the prediction and the Heaviside jump function. 
These measures all fail to consider whether the right direction of change is being taken, which can often be highly relevant in practice. The information about whether an estimator, be it a measurement device, forecast, or nowcast, can accurately predict an increase or decrease is crucial when making decisions based on the estimator's prediction results. In the following, we provide an overview of the characteristics and evaluations of measurement, forecasting, and nowcasting methods and show their relationships to trending.

@@

As outlined above, trending evaluation is crucial for measurements, predictions, and forecasts. 
However, regardless of the area of application, most conventional method comparisons and assessments consider local absolute differences in different ways without directly assessing whether the correct direction of change is being predicted or measured. In this paper, we want to complement the current evaluation measures with trending measurements and propose evaluation methods that assess the trending ability of a method.
